\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\title{Mixed Formatting Stress Test}
\author{QA Team}
\begin{document}
\maketitle

\section{Paragraph with Everything}
This paragraph has \textbf{bold text}, \textit{italic text}, \texttt{inline code},
a reference to Section 2, and some numbers like 3.14159 and 2.71828. It also
includes special characters: ampersand (\&), percent (5\%), dollar sign (\$100),
and various punctuation marks: semicolons; colons: dashes --- and ellipses\ldots

\section{Lists Followed by Paragraphs}
Here is a list:
\begin{itemize}
    \item \textbf{Bold list item} with explanation text
    \item \textit{Italic list item} with different formatting
    \item \texttt{Code list item} showing a command
\end{itemize}
And now we continue with a regular paragraph that follows the list. The converter
should correctly separate the list from this paragraph.

\section{Table Followed by Text}
\begin{table}[h]
\centering
\begin{tabular}{|l|r|}
\hline
\textbf{Metric} & \textbf{Value} \\
\hline
Precision & 94.2\% \\
Recall & 91.7\% \\
F1 Score & 92.9\% \\
\hline
\end{tabular}
\end{table}
The table above shows our evaluation metrics. As you can see, the system achieves
high precision and recall across all test cases.

\section{Multiple Paragraphs}
First paragraph of this section. It contains multiple sentences that should be
joined into a single paragraph in the Markdown output.

Second paragraph of this section. This tests that paragraph breaks are correctly
detected based on vertical spacing between text blocks.

Third paragraph. Short but distinct from the previous paragraphs.
\end{document}