\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\title{Multi-Level Heading Structure}
\author{Structure Tester}
\begin{document}
\maketitle

\section{Level 1: Architecture}
This section tests heading level detection across multiple depths.

\subsection{Level 2: Frontend}
The frontend uses vanilla HTML, CSS, and JavaScript.

\subsubsection{Level 3: HTML Structure}
The HTML file contains the drag-and-drop upload zone, progress display,
result view, and error handling sections.

\subsubsection{Level 3: CSS Design System}
CSS variables define the color palette, typography, spacing, and animations.
The design uses a dark theme with glassmorphism effects.

\subsection{Level 2: Backend}
The backend is built with FastAPI and Python.

\subsubsection{Level 3: API Routes}
Five routes handle the conversion lifecycle: upload, status, download Markdown,
download ZIP, and content preview.

\subsubsection{Level 3: Pipeline}
The conversion pipeline consists of six modular layers.

\section{Level 1: Testing}
Comprehensive tests verify each layer independently and the full pipeline
end-to-end.

\subsection{Level 2: Unit Tests}
Each pipeline module has dedicated unit tests with synthetic PDF fixtures.

\subsection{Level 2: Integration Tests}
End-to-end tests verify that real PDFs convert correctly with all content
preserved.

\section{Level 1: Deployment}
Deployment instructions for both development and production environments.
\end{document}